---
title: "Analysis.Rmd"
author: "Sarah Fite, Chris Havenstein"
date: "October 27, 2017"
output: github_document
---

# Analysis 

#### To begin the analysis, please set your working directory to the Analysis folder.


Depending on the directory you cloned the "MSDS 6372 - Project 2" into, the path to the "Analysis" folder should be similar to:

* ./root/MSDS 6372 - Project 2/Analysis

By modifying "Analysis.Rmd" in the Analysis folder, I set an absolute path to the Analysis folder on my computer.


```{r setwd}
setwd("C:\\Users\\Chris\\Desktop\\GIT home\\MSDS 6372 - Project 2\\Analysis")
```


Then, source Makefile.R

```{r makefile}
source("./Data/Makefile.R")

```
At this point, Makefile.R has completed running and has loaded the merged data for analysis.


Summary data:
```{r summary}
## The output will be:
## 1. "MergeData1.csv" -- merged  "CleanSpotPrices.csv" and "CleanOilGasRigsSplit.csv"
## 2. "MergeData2.csv" -- merged  "CleanSpotPrices.csv" and "CleanRigCountByTrajectory.csv"

## MergeData1 is MergeData1.csv
## MergeData2 is MergeData2.csv


#summary information of on MergeData1
print("MergeData1 includes Spot Prices and Oil and Gas Rig Split")
summary(MergeData1)

#summary information of MergeData2
print("MergeData2 includes Spot Prices and Rig Counts by Different Trajectories")
summary(MergeData2)
```


First 6 rows:
```{r head}
## The output will be:
## 1. "MergeData1.csv" -- merged  "CleanSpotPrices.csv" and "CleanOilGasRigsSplit.csv"
## 2. "MergeData2.csv" -- merged  "CleanSpotPrices.csv" and "CleanRigCountByTrajectory.csv"

## MergeData1 is MergeData1.csv
## MergeData2 is MergeData2.csv


#summary information of 1st six rows of on MergeData1
head(MergeData1)

#summary information 1st six rows of MergeData2
head(MergeData2)

```